\clearpage
## Cars

Here is some `cars` data:

```{r setcarscaption, echo=F, cache=F}
carsfigtabcap <- paste0("Caption text for Figure and Table")
carsfigcap <- 'A figure caption'
carstabcap <- 'A table caption'
```

```{r carsfigureandtable, fig.cap=carsfigtabcap, fig.subcap= c(carsfigcap, carstabcap), out.width = '.49\\linewidth', echo = F, fig.align='center', fig.pos='H'}
# from 
# https://stackoverflow.com/questions/53659160/r-markdown-positioning-table-and-plot-side-by-side
library(gridExtra)
library(grid)

# first plot
plot(mpg ~ hp, data = mtcars)

# second plot
grid.newpage()
grid.table(head(mtcars[,1:6]), theme = ttheme_minimal())
```

Look at Figure \ref{fig:carsfigureandtable}, it contains a figure (a) and a table (b).


Here is a box of text, using `ftext` command:


\sidenote{Don't take the following too seriously.}
\begin{ftext}
\tbontb{
\begin{minipage}{\textwidth}
There are three types of lies---lies, damn lies, and statistics. 
There are three types of lies---lies, damn lies, and statistics
There are three types of lies---lies, damn lies, and statistics
There are three types of lies---lies, damn lies, and statistics
There are three types of lies---lies, damn lies, and statistics
\end{minipage}
}
\end{ftext}

Here is an aligned equation, need to use in `ftext`:
\begin{ftext}
    \begin{align}
        \tbontb{y}  & \tbontb{= 2} \label{eqn:blank} \\
        z &= 2 
    \end{align}
\end{ftext}
Equation \eqref{eqn:blank} is blank in an align environment.



Using `fequation`:
\begin{fequation}
t = 1
\end{fequation}

It might be useful to include notes on the side, in the margin. These can be done using `sidenote`.
\sidenote{Here is an example of a sidenote}
And more text goes here, and one can read the note in the margin to remember certain points.


